AIMS Data Platform R Client Notebook Example

### 2019-11-07 docs/10.25845/5c09bf93f315d/example-1.Rmd
Updates

This example assumes you have obtained an *AIMS Data Platform API Key*.  See [here](index#usage-of-aims-dataplatform-api-key) to see what that means.  To download and run this example interactively in *R Studio* click on `Code -> Download Rmd` in the top right corner of this document.

>>>>

This example assumes you have obtained an [AIMS Data Platform API Key](https://aims.github.io/data-platform/key-request).  Further details about key usage can be found [here](https://aims.github.io/data-platform-r/index#usage-of-aims-dataplatform-api-key)

To download and run this example interactively in *R Studio* click on `Code -> Download Rmd` in the top right corner of this document.
